Effectiveness of community-based TURF-reserves in small-scale fisheries

### 2018-12-07 docs/manuscript.Rmd
Added reference to stefan to make explicit tat we dont refer to this reserves to close #52

Community-based TURF-reserves in small-scale fisheries can be helpful conservation and fishery management tools when appropriately implemented. As we move forward in marine conservation, we must recognize the value of local knowledge to identify priority areas for conservation, but without setting design principles aside. Lessons learned from these cases can guide implementation of community-based TURF-reserves elsewhere. For the particular case of the ones we evaluate, the possibility of expanding reserves or merging existing polygons into larger areas should be evaluated and proposed to the communities. Community-based marine reserves might have more benefits that result from indirect effects of the reserves, particularly providing resilience to shocks and management errors, and promoting social cohesion, which should be taken into account when evaluating the outcomes of TURF-reserves. Having full community support surely represents an advantage, but it is important that community-based TURF-reserves meet essential design principles such as size and placement so as to maximize their effectiveness.

>>>>

Community-based TURF-reserves in small-scale fisheries can be helpful conservation and fishery management tools when appropriately implemented \citep{gelcich_2015}. To implement them we must promote bottom-up design and implementation processes like the ones in the evaluated reserves, but without setting design principles aside. Lessons learned from these cases can guide implementation of community-based TURF-reserves elsewhere. For the particular case of the ones we evaluate, the possibility of expanding reserves or merging existing polygons into larger areas should be evaluated and proposed to the communities. Community-based marine reserves might have more benefits that result from indirect effects of the reserves, particularly providing resilience to shocks and management errors, and promoting social cohesion, which should be taken into account when evaluating the outcomes of TURF-reserves. Having full community support surely represents an advantage, but it is important that community-based TURF-reserves meet essential design principles such as size and placement so as to maximize their effectiveness.
